\documentclass[12pt,letterpaper]{article}

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[margin=1in]{geometry}
\usepackage{wrapfig}
\usepackage[justification=centering]{caption}
\usepackage[subnum]{cases}
\setlength{\parindent}{0pt}
\setlength{\parskip}{1em}
\usepackage{empheq}


\title{Agron 2002 Statistics\\ {\bf Lab Report 3}}
\date{30 March 2026}


\begin{document}
\maketitle
\section*{Instruction}
\begin{itemize}
    \item Paste your code (text, not screenshot) and output (screenshot) in a pdf file
    \item Format: \textbf{pdf} only
    \item Deadline: 2026/04/05 (SUN) 23:59
    \item Late submission is not accepted
\end{itemize}


\section*{Exercise 1}
A manufacturing plant produces electronic components. Historically, 5\% of the components are defective. You take a random sample of 100 components from the assembly line.

\textbf{a.} What is the exact probability that you find exactly 3 defective components in your sample of 100?

\textbf{b.} What is the probability that you find 5 or more defective components?

\textbf{c.} You want to define a "threshold" for a bad batch. Below what number of defects do the best 90\% of all samples fall? [Hint: Find the 90th percentile]

\textbf{d.} Simulate the inspection process for 10 different days (10 samples of 100). How many defects are found in each of those 10 simulated samples?

\section*{Exercise 2}
An internal study by the Technology Services department at Lahey Electronics revealed
company employees receive an average of two non-work-related emails per hour. Assume the arrival of these e-mails is approximated by the Poisson distribution.

\textbf{a.} What is the probability Linda Lahey, company president, received exactly one non-work-related e-mail between 4 p.m. and 5 p.m. yesterday?

\textbf{b.} What is the probability she received five or more non-work-related e-mails during the same period?

\textbf{c.} What is the probability she did not receive any non-work-related e-mails during the
period?

\section*{Exercise 3}
The average number of acres burned by forest and range fires in a large New Mexico county is 4,300 acres per year, with a standard deviation of 750 acres. The distribution of the number of acres burned is normal.

\textbf{a.} What is the probability that between 2,500 and 4,200 acres will be burned in any given year? 

\textbf{b.}  What number of burnt acres corresponds to the 38th percentile? 


\end{document}